## advance 

The `advance` function constructs the initial abundance for the next
annual projection given the projected abundances for the current year.
Essentially, `advance` advances the final abundance of each cohort by
an age class filling the first age class with recruits. If the last
age class is a "plus" class, the surviving individuals of the plus
class are retained when the classes advance, otherwise these
individuals are lost to the population.

#### Setup

Define age classes and within year time steps
```{r}
## Daily time steps and 7 age classes
nsteps <- 365
Ages <- 2:8
Days <- seq(0,1,length=nsteps+1)
h <- 1/nsteps
```

Create matrices of age, length and weight for each time step and age class
```{r}
## Ages
ages <- outer(Days,Ages,FUN="+")
## Age-length and length-weight conversions
ls <- vonBertalanffyAL(ages,t0=0.0667,K=0.5,Linf=500)
ws <- powerLW(ls,9E-10,3.32)
```

Define the intra-annual natural mortality, its integral and the annual scaling
```{r}
## Constant intra-annual natural mortality
ms <- matrix(1,nsteps+1,length(Ages))
ms <- ms/mean(trapz(ms,h))
Ms <- ctrapz(ms,h)
Msf <- final(Ms)
M <- 0.1
```

Define the intra-annual fishing mortality, its integral and the annual
scaling, assuming fishing occurs on days 80 to 119 and there is length
based selectivity
```{r}
## Define fishing mortalities - mid-year fishing with length based selectivity 
fs <- double(nsteps+1)
fs[81:220] <- 1
fs <- fs/trapz(fs,h)
fs <- fs*rampOgive(ls,420,30)
Fs <- ctrapz(fs,h)
Fsf <- final(Fs)
F <- 0.2
```

Compute an intial age structure assuming constant mortalities
```{r}
## Deterministic initial age structure
N0 <- ageStructureD(M*Msf,F*Fsf)
N0
```

Project forward for a single year with known mortalities
```{r}
## Annual projection from N0
pr <- project(ws,M*Ms,F*Fs,F*fs,Nref=N0)
```

The projected final abundance is
```{r}
## Final abundance
pr$N[nsteps+1,]
```

#### Advance

Advance the final cohort numbers by one age class to form the initial
numbers for the next projection.  If the final age class is not a plus
group individuals in the final age class are discarded in the advancement
```{r}
## Initial abundance for next projection assuming no plus group
advance(pr$N,R=1)
```

If the final age class is a plus group the individuals in the final
age class are retained
```{r}
## Initial abundance for next projection assuming plus group
advance(pr$N,R=1,plus=TRUE)
```


#### Project without plus class

Project forward 10 years from a virgin stock assuming constant fishing
mortality, collating annual abundance, biomass and yield, assuming the
final class is not a plus class.

Create matrices to store annual projections
```{r}
## Ten year projection from virgin stock collating final annual
## abundance, biomass and yield
Years <- 1:10
Nf <- Bf <- Yf <- matrix(NA,length(Years),length(Ages))
```


Compute an equilibrium age structure assuming constant natural mortality
and no fishing, assuming no plus class and 8000 recruits per year.
```{r}
## Deterministic initial age structure assuming no fishing and 8000
## new recruits each year
N0 <- ageStructureD(M*Msf,R=8000)
```

For each year, project forward from the initial abundance assuming
constant fishing mortality, update the the initial abundance for the
next projection assuming 8000 new recruits, and record the final
abundance, biomass and yield from the projection
```{r}
## Project forward with constant fishing mortality
for(k in 1:nrow(Nf)) {
  pr <- project(ws,M*Ms,F*Fs,F*fs,Nref=N0,yield=1)
  N0 <- advance(pr$N,R=8000)
  Nf[k,] <- final(pr$N)
  Bf[k,] <- final(pr$B)
  Yf[k,] <- pr$Y
}
```

Plot final abundance, biomass and yield for each year by age class
```{r,fig.show="hold"}
## Plot annual abundance, biomass and yield
opar <- par(mfrow=c(2,2),mar=c(5,4,2,2)+0.1)
pal <- hcl(h=seq(15,375,length=8)[1:7],l=65,c=100)
matplot(Years,Nf,xlab="Year",ylab="Abundance",type="l",lty=1,col=pal)
matplot(Years,Bf,xlab="Year",ylab="Biomass",type="l",lty=1,col=pal)
matplot(Years,Yf,xlab="Year",ylab="Yield",type="l",lty=1,col=pal)
par(opar)
```


#### Project with plus class

Project forward 10 years from a virgin stock assuming constant fishing
mortality, collating annual abundance, biomass and yield, assuming the
final class is a plus class.

Create matrices to store annual projections
```{r}
## Ten year projection from virgin stock collating final annual
## abundance, biomass and yield
Years <- 1:10
Nf <- Bf <- Yf <- matrix(NA,length(Years),length(Ages))
```


Compute an equilibrium age structure assuming constant natural mortality
and no fishing with 8000 recruits per year. Treat the last class as a
plus group assuming an additional 50 age classes are aggregated into
the plus class
```{r}
## Deterministic initial age structure assuming no fishing, 8000
## new recruits each year and a plus class
N0 <- ageStructureD(M*Msf,R=8000,plus=50)
```

For each year, project forward from the initial abundance assuming
constant fishing mortality, update the the initial abundance for the
next projection assuming 8000 new recruits and assuming the last class
is a plus class, and record the final abundance, biomass and yield
from the projection
```{r}
## Project forward with constant fishing mortality assuming plus class
for(k in 1:nrow(Nf)) {
  pr <- project(ws,M*Ms,F*Fs,F*fs,Nref=N0,yield=1)
  N0 <- advance(pr$N,R=8000,plus=TRUE)
  Nf[k,] <- final(pr$N)
  Bf[k,] <- final(pr$B)
  Yf[k,] <- pr$Y
}
```

Plot final abundance, biomass and yield for each year by age class
```{r,fig.show="hold"}
## Plot annual abundance, biomass and yield
opar <- par(mfrow=c(2,2),mar=c(5,4,2,2)+0.1)
pal <- hcl(h=seq(15,375,length=8)[1:7],l=65,c=100)
matplot(Years,Nf,xlab="Year",ylab="Abundance",type="l",lty=1,col=pal)
matplot(Years,Bf,xlab="Year",ylab="Biomass",type="l",lty=1,col=pal)
matplot(Years,Yf,xlab="Year",ylab="Yield",type="l",lty=1,col=pal)
par(opar)
```
