## ageStructureD

The `ageStructureD` function computes the equilibrium age structure of
the population assuming the recruitment and the annual scalings of
natural and fishing mortality are constant

#### Setup

Define age classes and within year time steps
```{r}
## Daily time steps and 7 age classes
nsteps <- 365
Ages <- 2:8
Days <- seq(0,1,length=nsteps+1)
h <- 1/nsteps
```

Create matrices of age, length and weight for each time step and age class
```{r}
## Ages
ages <- outer(Days,Ages,FUN="+")
## Age-length and length-weight conversions
ls <- vonBertalanffyAL(ages,t0=0.0667,K=0.5,Linf=500)
ws <- powerLW(ls,9E-10,3.32)
```

Define the intra-annual natural mortality, its integral and the annual scaling
```{r}
## Constant intra-annual natural mortality
ms <- matrix(1,nsteps+1,length(Ages))
ms <- ms/mean(trapz(ms,h))
Ms <- ctrapz(ms,h)
Msf <- final(Ms)
M <- 0.2
```

#### Age structure

Compute and initial age structure assuming no fishing and no plus group
```{r}
## Deterministic initial age structure assuming no fishing and no plus
## group
N0 <- ageStructureD(M*Msf)
N0
```

Projecting forward with the same mortality used to compute the
equilibrium age structure should leave the abundances stable
```{r}
## Annual projection from N0
pr <- project(ws,M*Ms,Nref=N0)
## Initial and final abundance
pr$N[c(1,nsteps+1),]
```

The deterministic age structure should match the stochastic age structure for
constant recruitment and mortalities.  If the last class is not a plus
class
```{r}
## Deterministic initial age structure with no plus class
ageStructureD(M*Msf)
## Stochastic initial age structure with constant recruitment
ageStructureS(rep(1,20),Msf,M)
```

If the last class is a plus class aggregrating 50 additional age classes
```{r}
## Deterministic initial age structure assuming the plus class
## aggregates 50 additional age classes
ageStructureD(M*Msf,plus=20)
## Stochastic initial age structure with constant recruitment with
## plus class
ageStructureS(rep(1,7+20),Msf,M,plus=TRUE)
```

For the deterministic computation, the plus class can contain an infinite number
of additional age classes
```{r}
## Deterministic initial age structure assuming no upper limit on age
ageStructureD(M*Msf,plus=Inf)
```


#### Scaling

By default the scaling of the abundances are determined by the level
of recruitment
```{r}
## Scale to recruitment
N0 <- ageStructureD(M*Msf,R=8000)
N0
```

Alternately, the age structure can used as a relative abundances and
scaled to a mid-year survey biomass with `project`
```{r}
## Scale age structure to biomass estimated from a five day mid-year
## survey (days 150 to 154)
Bsurvey <- 15000 
N0 <- ageStructureD(M*Msf)
pr <- project(ws,M*Ms,0,0,Nref=N0,nref=1,Bref=Bsurvey,bref=151:155)
N0 <- initial(pr$N)
N0
```
