## ageStructureS

The `ageStructureS` function computes a stochastic initial age
structure of the population assuming both the recruitment and the
annual scalings of natural and fishing mortalities may vary
inter-annually.

#### Setup

Define age classes and within year time steps
```{r}
## Daily time steps and 7 age classes
nsteps <- 365
Ages <- 2:8
Days <- seq(0,1,length=nsteps+1)
h <- 1/nsteps
```

Create matrices of age, length and weight for each time step and age class
```{r}
## Ages
ages <- outer(Days,Ages,FUN="+")
## Age-length and length-weight conversions
ls <- vonBertalanffyAL(ages,t0=0.0667,K=0.5,Linf=500)
ws <- powerLW(ls,9E-10,3.32)
```

Define the intra-annual natural mortality, its integral and the annual scaling
```{r}
## Constant intra-annual natural mortality
ms <- matrix(1,nsteps+1,length(Ages))
ms <- ms/mean(trapz(ms,h))
Ms <- ctrapz(ms,h)
Msf <- final(Ms)
M <- 0.2
```

#### Log Normal Recruitment

Compute an initial age structure assuming numbers of recruits are log
Normally distributed.  Recruitment must be simulated for at least as
many years as there are age classes with non neglible abundance in the
population (including age classes aggregated into the plus group).
```{r}
## Stochastic initial age structure with log Normal recruitment
ageStructureS(rlnorm(8,log(10),0.2),Msf,M)
```

Compare 100 stochastic structures based on log Normal recruitment to
the corresponding deterministic age structure
```{r}
## Plot 100 replicates
Rs <- replicate(100,ageStructureS(rlnorm(8,log(10),0.2),Msf,M))
matplot(Rs,type="l",lty=1,col=rgb(0,0,0,0.1),xlab="Age",ylab="Abundance")
lines(ageStructureD(M*Msf,R=exp(log(10)+0.1^2/2)),col="firebrick")
```

It can be more efficient to base each simulated profile on the
previous but simulate forward fewer years. 
```{r}
Rs <- matrix(0,length(Ages),100)
Rs[,1] <- ageStructureS(rlnorm(8,log(10),0.2),Msf,M)
for(k in 2:ncol(Rs))
  Rs[,k] <- ageStructureS(rlnorm(8,log(10),0.2),Msf,M,N0=Rs[,k-1])
matplot(Rs,type="l",lty=1,col=rgb(0,0,0,0.1),xlab="Age",ylab="Abundance")
lines(ageStructureD(M*Msf,R=exp(log(10)+0.1^2/2)),col="firebrick")
```
