## powerLW

The GYM uses a simple power law model
\[
W = a L^b
\]
to map lengths to weights.

The `powerLW` function implements the power law model as parameterized
in the GYM
```{r}
len <- seq(150,450,50)

## Convert length to weight
wgt <- powerLW(len,9.0E-10,3.32)
wgt
```

and `powerWL` is the inverse mapping
```{r}
## Convert weigth to length
len <- powerWL(wgt,9.0E-10,3.32)
len
```

#### Weight at age

Define age classes and within year time steps
```{r}
## Daily time steps and 7 age classes
nsteps <- 365
Ages <- 2:8
Days <- seq(0,1,length=nsteps+1)
h <- 1/nsteps
```

Create a matrix of the age at each time step of each age class
```{r}
## Ages
ages <- outer(Days,Ages,FUN="+")
```

Use a von Bertalanffy length at age relationship to create a matrix of
the length at each time step of each age class
```{r}
## Age-length conversion
ls <- vonBertalanffyAL(ages,t0=0.0667,K=0.5,Linf=500)
```

and a power law weight-length relationship to create a matrix of the
weight at each time step of each age class
```{r}
## Length-weight conversion
ws <- powerLW(ls,9E-10,3.32)
matplot(Days,ws,type="l",lty=1,xlab="Day",ylab="Weight",main="Weight at Age")
```
