## prBootstrap

Let \(A_{k}\) be the number of individuals in age class \(k\) and define
\[
R = \frac{A_{r}}{\sum_{k=r} A_{k}}
\]
the number of individuals in age class \(r\) as a poportion of all
individuals of that age or older.

The proportional1 recruitment model assumes estimates of the mean and
variance of \(R\) from independent surveys.  To allow for uncertainty
in these estimates, `prBootstrap` uses parametric bootstrap to
simulates new values for the mean and variance of \(R\) that are
consistent with the observed values.

#### Setup

Define age classes and within year time steps
```{r}
## Daily time steps and 7 age classes
nsteps <- 365
Ages <- 2:8
Days <- seq(0,1,length=nsteps+1)
h <- 1/nsteps
```

Create matrices of age, length and weight for each time step and age class
```{r}
## Ages
ages <- outer(Days,Ages,FUN="+")
## Age-length and length-weight conversions
ls <- vonBertalanffyAL(ages,t0=0.0667,K=0.5,Linf=500)
ws <- powerLW(ls,9E-10,3.32)
```

Define the intra-annual natural mortality, its integral and the annual scaling
```{r}
## Constant intra-annual natural mortality
ms <- matrix(1,nsteps+1,length(Ages))
ms <- ms/mean(trapz(ms,h))
Ms <- ctrapz(ms,h)
Msf <- final(Ms)
M <- 0.2
```


#### Inverse Beta

Generate model parameters from the observed mean and variance of R
assuming the Inverse Beta model
```{r}
## Compute model parameters that give mean R = 0.3 and var R = 0.01,
## when R is the proportion of recruits in the population
ps <- prRecruitParsIB(mnR=0.3,vrR=0.01,Msf)
```

Simulate a new values for the mean and variance on which subsequent
projections could be based, assuming the original estimates were
generated from 17 independent survey
```{r}
## Simulate new mean and variance for 17 surveys
prBootstrap(prRecruitsIB,ps,17,Msf)
```

Generate 2000 bootstrap samples and examine the distribution of the
simulated mean and variance
```{r,fig.show="hold"}
## Distribution of 2000 samples
bs <- replicate(2000,unlist(prBootstrap(prRecruitsIB,ps,17,Msf)))
opar <- par(mfrow=c(1,2))
hist(bs[1,],50,xlab="Mean R",main="")
abline(v=median(bs[1,]),col="red")
hist(bs[2,],50,xlab="Variance R",main="")
abline(v=median(bs[2,]),col="red")
par(opar)
```


#### Gamma

Generate model parameters from the observed mean and variance of R
assuming the Gamma model
```{r}
## Compute model parameters that give mean R = 0.3 and var R = 0.01,
## when R is the proportion of recruits in the population
ps <- prRecruitParsG(mnR=0.3,vrR=0.01,Msf)
```

Simulate a new values for the mean and variance on which subsequent
projections could be based, assuming the original estimates were
generated from 17 independent survey
```{r}
## Simulate new mean and variance for 17 surveys
prBootstrap(prRecruitsG,ps,17,Msf)
```

Generate 2000 bootstrap samples and examine the distribution of the
simulated mean and variance
```{r,fig.show="hold"}
## Distribution of 2000 samples
bs <- replicate(2000,unlist(prBootstrap(prRecruitsG,ps,17,Msf)))
opar <- par(mfrow=c(1,2))
hist(bs[1,],50,xlab="Mean R",main="")
abline(v=median(bs[1,]),col="red")
hist(bs[2,],50,xlab="Variance R",main="")
abline(v=median(bs[2,]),col="red")
par(opar)
```


#### Log Normal

Generate model parameters from the observed mean and variance of R
assuming the log Normal model
```{r}
## Compute model parameters that give mean R = 0.3 and var R = 0.01,
## when R is the proportion of recruits in the population
ps <- prRecruitParsLN(mnR=0.3,vrR=0.01,Msf)
```

Simulate a new values for the mean and variance on which subsequent
projections could be based, assuming the original estimates were
generated from 17 independent survey
```{r}
## Simulate new mean and variance for 17 surveys
prBootstrap(prRecruitsLN,ps,17,Msf)
```

Generate 2000 bootstrap samples and examine the distribution of the
simulated mean and variance
```{r,fig.show="hold"}
## Distribution of 2000 samples
bs <- replicate(2000,unlist(prBootstrap(prRecruitsLN,ps,17,Msf)))
opar <- par(mfrow=c(1,2))
hist(bs[1,],50,xlab="Mean R",main="")
abline(v=median(bs[1,]),col="red")
hist(bs[2,],50,xlab="Variance R",main="")
abline(v=median(bs[2,]),col="red")
par(opar)
```


#### GYM

Generate model parameters from the observed mean and variance of R
assuming the model implemented in the GYM
```{r}
## Compute model parameters that give mean R = 0.3 and var R = 0.01,
## when R is the proportion of recruits in the population
ps <- prRecruitParsGYM(mnR=0.3,vrR=0.01,Msf)
```

Simulate a new values for the mean and variance on which subsequent
projections could be based, assuming the original estimates were
generated from 17 independent survey
```{r}
## Simulate new mean and variance for 17 surveys
prBootstrap(prRecruitsGYM,ps,17,Msf)
```

Generate 2000 bootstrap samples and examine the distribution of the
simulated mean and variance
```{r,fig.show="hold"}
## Distribution of 2000 samples
bs <- replicate(2000,unlist(prBootstrap(prRecruitsGYM,ps,17,Msf)))
opar <- par(mfrow=c(1,2))
hist(bs[1,],50,xlab="Mean R",main="")
abline(v=median(bs[1,]),col="red")
hist(bs[2,],50,xlab="Variance R",main="")
abline(v=median(bs[2,]),col="red")
par(opar)
```
