## prRecruitsGYM

Grym offers the same proprtional recruitment model based on the Beta
distribution offered in the GYM.

Let \(A_{k}\) be the number of individuals in age class \(k\) and define
\[
R = \frac{A_{r}}{\sum_{k=r} A_{k}}
\]
the number of individuals in age class \(r\) as a poportion of all
individuals of that age or older.  Given estimates of the mean and
variance of \(R) from independent surveys, the proportional
recruitment model determines the scaling of natural mortality M and
the distribution of random recruits that will reproduce the observed
mean and variance of R.

#### Setup

Define age classes and within year time steps
```{r}
## Daily time steps and 7 age classes
nsteps <- 365
Ages <- 2:8
Days <- seq(0,1,length=nsteps+1)
h <- 1/nsteps
```

Create matrices of age, length and weight for each time step and age class
```{r}
## Ages
ages <- outer(Days,Ages,FUN="+")
## Age-length and length-weight conversions
ls <- vonBertalanffyAL(ages,t0=0.0667,K=0.5,Linf=500)
ws <- powerLW(ls,9E-10,3.32)
```

Define the intra-annual natural mortality, its integral and the annual scaling
```{r}
## Constant intra-annual natural mortality
ms <- matrix(1,nsteps+1,length(Ages))
ms <- ms/mean(trapz(ms,h))
Ms <- ctrapz(ms,h)
Msf <- final(Ms)
M <- 0.2
```


#### GYM

Let \(R\) be the proportion of the number of recruits as a fraction of the
total population.

Generate model parameters from the mean and variance of R.  This
computes an estimate of the scaling of natural mortality required to
reproduce the observed \(R\).
```{r}
## Compute model parameters that give mean R = 0.3 and var R = 0.01,
## when R is the proportion of recruits in the population
ps <- prRecruitParsGYM(mnR=0.3,vrR=0.01,Msf)
## Estimated natural mortality scaling
ps$M
```

Compute the median number of recruits
```{r}
## Median number of recruits
prRecruitsQuantileGYM(0.5,ps,mnA=100)
```

Random numbers of recruits are generated from the estimate parameters
```{r}
## Ten random recruit numbers
prRecruitsGYM(10,ps,mnA=100)
```

Check the random numbers of recruits have the required mean
```{r} 
## Mean number of recruits
mean(prRecruitsGYM(10000,ps,mnA=100))
```

Simulate the 1000 stochastic age profiles with this distributionof
recruits and check the the observed mean and variance of R are reproduced
```{r}
## Simulate age profiles and calculate R
N <- matrix(0,10000,ncol(Ms))
for(k in 1:nrow(N))
  N[k,] <- ageStructureS(prRecruitsGYM(10,ps,mnA=100),Msf,ps$M)
R <- N[,1]/rowSums(N)
## Estimate mean and variance of R
mean(R)
var(R)
```

The random recruits have a scaled inverse Beta distribution 
```{r}
## Histogram of simulated recruitments
rs <- prRecruitsGYM(100000,ps,mnA=100)
hist(rs[rs < 350],seq(0,350,5),freq=FALSE,xlab="Recruits",main="GYM")
```


Repeat for the case where R is the proportion of individuals in age
class 3 as a fraction of individuals of that age or older,
```{r}
## Compute model parameters that give mean R = 0.3 and var R = 0.01,
## when R is the proportion of individual in age class 3 as a fraction
## of individuals that are that age or older
ps <- prRecruitParsGYM(mnR=0.3,vrR=0.01,Msf,r=3)
## Estimated natural mortality scaling
ps$M
```

Compute the median number of recruits
```{r}
## Median number of recruits
prRecruitsQuantileGYM(0.5,ps,mnA=100)
```

Random numbers of recruits are generated from the estimate parameters
```{r}
## Ten random recruit numbers
prRecruitsGYM(10,ps,mnA=100)
```

Check the random numbers of recruits have the required mean
```{r} 
## Mean number of recruits
mean(prRecruitsGYM(10000,ps,mnA=100))
```

Simulate the 1000 stochastic age profiles with this distributionof
recruits and check the the observed mean and variance of R are reproduced
```{r}
## Simulate age profiles and calculate R
N <- matrix(0,100000,ncol(Ms))
for(k in 1:nrow(N))
  N[k,] <- ageStructureS(prRecruitsGYM(10,ps,mnA=100),Msf,ps$M)
R <- N[,3]/rowSums(N[,3:7])
## Estimate mean and variance of R
mean(R)
var(R)
```

