## prRecruits

Grym offers several variants of the proportional recruitment model
implemented in the GYM.

Let \(A_{k}\) be the number of individuals in age class \(k\) and define
\[
R = \frac{A_{r}}{\sum_{k=r} A_{k}}
\]
the number of individuals in age class \(r\) as a proportion of all
individuals of that age or older.  Given estimates of the mean and
variance of \(R\) from independent surveys, the proportional
recruitment model determines the scaling of natural mortality M and
the distribution of random recruits that will reproduce the observed
mean and variance of R.

#### Setup

Define age classes and within year time steps
```{r}
## Daily time steps and 7 age classes
nsteps <- 365
Ages <- 2:8
Days <- seq(0,1,length=nsteps+1)
h <- 1/nsteps
```

Create matrices of age, length and weight for each time step and age class
```{r}
## Ages
ages <- outer(Days,Ages,FUN="+")
## Age-length and length-weight conversions
ls <- vonBertalanffyAL(ages,t0=0.0667,K=0.5,Linf=500)
ws <- powerLW(ls,9E-10,3.32)
```

Define the intra-annual natural mortality, its integral and the annual scaling
```{r}
## Constant intra-annual natural mortality
ms <- matrix(1,nsteps+1,length(Ages))
ms <- ms/mean(trapz(ms,h))
Ms <- ctrapz(ms,h)
Msf <- final(Ms)
```

Let \(R\) be the proportion of the number of recruits as a fraction of the
total population.


#### Inverse Beta

Generate model parameters from the mean and variance of \(R\).  This
computes an estimate of the scaling of natural mortality required to
reproduce the observed \(R\).
```{r}
## Compute model parameters that give mean R = 0.3 and var R = 0.1,
## where R is the proportion of recruits in the population
ps <- prRecruitParsIB(Msf,mnR=0.3,vrR=0.01)
## Estimated natural mortality scaling
ps$M
```

Compute the median number of recruits
```{r}
## Median number of recruits
prRecruitsQuantileIB(0.5,ps,mnA=100)
```

Random numbers of recruits are generated from the estimated parameters
```{r}
## Ten random recruit numbers
prRecruitsIB(10,ps,mnA=100)
```

Check the random numbers of recruits have the required mean
```{r}
## Mean number of recruits
mean(prRecruitsIB(10000,ps,mnA=100))
```

Simulate the 10000 stochastic age profiles with this distribution of
recruits and check the the observed mean and variance of \(R\) are reproduced
```{r}
## Simulate age profiles and calculate R
N <- matrix(0,10000,ncol(Ms))
for(k in 1:nrow(N))
  N[k,] <- ageStructureS(prRecruitsIB(ncol(Ms),ps,mnA=100),Msf,ps$M)
R <- N[,1]/rowSums(N)
## Estimate mean and variance of R
mean(R)
var(R)
```

The random recruits have a scaled inverse Beta distribution 
```{r}
## Histogram of simulated recruitments
rs <- prRecruitsIB(100000,ps,mnA=100)
hist(rs[rs < 350],seq(0,350,5),freq=FALSE,xlab="Recruits",main="Inverse Beta")
```


Repeat for the case where R is the proportion of individuals in age
class 3 as a fraction of individuals of that age or older,
```{r}
## Compute model parameters that give mean R = 0.3 and var R = 0.01,
## where R is the proportion of individual in age class 3 as a fraction
## of individuals that are that age or older
ps <- prRecruitParsIB(Msf,mnR=0.3,vrR=0.01,r=3)
## Estimated natural mortality scaling
ps$M
```

Compute the median number of recruits
```{r}
## Median number of recruits
prRecruitsQuantileIB(0.5,ps,mnA=100)
```

Random numbers of recruits are generated from the estimated parameters
```{r}
## Ten random recruit numbers
prRecruitsIB(10,ps,mnA=100)
```

Check the random numbers of recruits have the required mean
```{r}
## Mean number of recruits
mean(prRecruitsIB(10000,ps,mnA=100))
```

Simulate the 10000 stochastic age profiles with this distribution of
recruits and check the the observed mean and variance of \(R\) are reproduced
```{r}
## Simulate age profiles and calculate R
N <- matrix(0,10000,ncol(Ms))
for(k in 1:nrow(N))
  N[k,] <- ageStructureS(prRecruitsIB(ncol(Ms),ps,mnA=100),Msf,ps$M)
R <- N[,3]/rowSums(N[,3:7])
## Estimate mean and variance of R
mean(R)
var(R)
```


#### Gamma

Generate model parameters from the mean and variance of \(R\).  This
computes an estimate of the scaling of natural mortality required to
reproduce the observed \(R\).
```{r}
## Compute model parameters that give mean R = 0.3 and var R = 0.01,
## where R is the proportion of recruits in the population
ps <- prRecruitParsG(Msf,mnR=0.3,vrR=0.01)
## Estimated natural mortality scaling
ps$M
```

Compute the median number of recruits
```{r}
## Median number of recruits
prRecruitsQuantileG(0.5,ps,mnA=100)
```

Random numbers of recruits are generated from the estimated parameters
```{r}
## Ten random recruit numbers
prRecruitsG(10,ps,mnA=100)
```

Check the random numbers of recruits have the required mean
```{r}
## Mean number of recruits
mean(prRecruitsG(10000,ps,mnA=100))
```

Simulate the 10000 stochastic age profiles with this distribution of
recruits and check the the observed mean and variance of \(R\) are reproduced
```{r}
## Simulate age profiles and calculate R
N <- matrix(0,10000,ncol(Ms))
for(k in 1:nrow(N))
  N[k,] <- ageStructureS(prRecruitsG(ncol(Ms),ps,mnA=100),Msf,ps$M)
R <- N[,1]/rowSums(N)
## Estimate mean and variance of R
mean(R)
var(R)
```

The random recruits have a scaled Gamma distribution 
```{r}
## Histogram of simulated recruitments
rs <- prRecruitsG(100000,ps,mnA=100)
hist(rs[rs < 350],seq(0,350,5),freq=FALSE,xlab="Recruits",main="Gamma")
```

Repeat for the case where R is the proportion of individuals in age
class 3 as a fraction of individuals of that age or older,
```{r}
## Compute model parameters that give mean R = 0.3 and var R = 0.01,
## where R is the proportion of individual in age class 3 as a fraction
## of individuals that are that age or older
ps <- prRecruitParsG(Msf,mnR=0.3,vrR=0.01,r=3)
## Estimated natural mortality scaling
ps$M
```

Compute the median number of recruits
```{r}
## Median number of recruits
prRecruitsQuantileG(0.5,ps,mnA=100)
```

Random numbers of recruits are generated from the estimated parameters
```{r}
## Ten random recruit numbers
prRecruitsG(10,ps,mnA=100)
```

Check the random numbers of recruits have the required mean
```{r}
## Mean number of recruits
mean(prRecruitsG(10000,ps,mnA=100))
```

Simulate the 10000 stochastic age profiles with this distribution of
recruits and check the the observed mean and variance of \(R\) are reproduced
```{r}
## Simulate age profiles and calculate R
N <- matrix(0,10000,ncol(Ms))
for(k in 1:nrow(N))
  N[k,] <- ageStructureS(prRecruitsG(ncol(Ms),ps,mnA=100),Msf,ps$M)
R <- N[,3]/rowSums(N[,3:7])
## Estimate mean and variance of R
mean(R)
var(R)
```


#### Log Normal

Generate model parameters from the mean and variance of \(R\).  This
computes an estimate of the scaling of natural mortality required to
reproduce the observed \(R\).
```{r}
## Compute model parameters that give mean R = 0.3 and var R = 0.01,
## where R is the proportion of recruits in the population
ps <- prRecruitParsLN(Msf,mnR=0.3,vrR=0.01)
## Estimated natural mortality scaling
ps$M
```

Compute the median number of recruits
```{r}
## Median number of recruits
prRecruitsQuantileLN(0.5,ps,mnA=100)
```

Random numbers of recruits are generated from the estimated parameters
```{r}
## Ten random recruit numbers
prRecruitsLN(10,ps,mnA=100)
```

Check the random numbers of recruits have the required mean
```{r}
## Mean number of recruits
mean(prRecruitsLN(10000,ps,mnA=100))
```

Simulate the 10000 stochastic age profiles with this distribution of
recruits and check the the observed mean and variance of \(R\) are reproduced
```{r}
## Simulate age profiles and calculate R
N <- matrix(0,10000,ncol(Ms))
for(k in 1:nrow(N))
  N[k,] <- ageStructureS(prRecruitsLN(ncol(Ms),ps,mnA=100),Msf,ps$M)
R <- N[,1]/rowSums(N)
## Estimate mean and variance of R
mean(R)
var(R)
```

The random recruits have a scaled log Normal distribution 
```{r}
## Histogram of simulated recruitments
rs <- prRecruitsLN(100000,ps,mnA=100)
hist(rs[rs < 350],seq(0,350,5),freq=FALSE,xlab="Recruits",main="Log Normal")
```


Repeat for the case where R is the proportion of individuals in age
class 3 as a fraction of individuals of that age or older,
```{r}
## Compute model parameters that give mean R = 0.3 and var R = 0.01,
## where R is the proportion of individual in age class 3 as a fraction
## of individuals that are that age or older
ps <- prRecruitParsLN(Msf,mnR=0.3,vrR=0.01,r=3)
## Estimated natural mortality scaling
ps$M
```

Compute the median number of recruits
```{r}
## Median number of recruits
prRecruitsQuantileLN(0.5,ps,mnA=100)
```

Random numbers of recruits are generated from the estimated parameters
```{r}
## Ten random recruit numbers
prRecruitsLN(10,ps,mnA=100)
```

Check the random numbers of recruits have the required mean
```{r}
## Mean number of recruits
mean(prRecruitsLN(10000,ps,mnA=100))
```

Simulate the 10000 stochastic age profiles with this distribution of
recruits and check the the observed mean and variance of \(R\) are reproduced
```{r}
## Simulate age profiles and calculate R
N <- matrix(0,10000,ncol(Ms))
for(k in 1:nrow(N))
  N[k,] <- ageStructureS(prRecruitsLN(ncol(Ms),ps,mnA=100),Msf,ps$M)
R <- N[,3]/rowSums(N[,3:7])
## Estimate mean and variance of R
mean(R)
var(R)
```


#### Delta Inverse Beta

The Delta-Inverse Beta model may provide a closer fit to abundance
data with a zero-inflated distribution.

Generate model parameters from the mean and variance of \(R\).  This
computes an estimate of the scaling of natural mortality required to
reproduce the observed \(R\).
```{r}
## Compute model parameters that give mean R = 0.3 and var R = 0.2,
## where R is the proportion of recruits in the population, assuming
## zero recruitment occurs with probability 0.4
ps <- prRecruitParsDIB(Msf,mnR=0.3,vrR=0.2,p=0.4)
## Estimated natural mortality scaling
ps$M
```

Compute the median number of recruits
```{r}
## Median number of recruits
prRecruitsQuantileDIB(0.5,ps,mnA=100)
```

Random numbers of recruits are generated from the estimated parameters
```{r}
## Ten random recruit numbers
prRecruitsDIB(10,ps,mnA=100)
```

Check the random numbers of recruits have the required mean
```{r}
## Mean number of recruits
mean(prRecruitsDIB(10000,ps,mnA=100))
```

Simulate the 10000 stochastic age profiles with this distribution of
recruits and check the the observed mean and variance of \(R\) are reproduced
```{r}
## Simulate age profiles and calculate R
N <- matrix(0,10000,ncol(Ms))
for(k in 1:nrow(N))
  N[k,] <- ageStructureS(prRecruitsDIB(ncol(Ms),ps,mnA=100),Msf,ps$M)
R <- N[,1]/rowSums(N)
## Estimate mean and variance of R
mean(R,na.rm=TRUE)
var(R,na.rm=TRUE)
```

The random non-zero recruitment events have a scaled Inverse Beta distribution
```{r}
## Histogram of simulated recruitments
rs <- prRecruitsDIB(100000,ps,mnA=100)
hist(rs[rs >0 & rs < 600],seq(0,600,5),freq=FALSE,xlab="Recruits",main="Delta Inverse Beta")
```

But there are many zero recruitment events
```{r}
## Fraction of zero recruitments
mean(rs==0)
```

Repeat for the case where R is the proportion of individuals in age
class 3 as a fraction of individuals of that age or older,
```{r}
## Compute model parameters that give mean R = 0.3 and var R = 0.2,
## where R is the proportion of individual in age class 3 as a fraction
## of individuals that are that age or older, assuming
## recruitment occurs with probability 0.4
ps <- prRecruitParsDIB(Msf,mnR=0.3,vrR=0.2,p=0.4,r=3)
## Estimated natural mortality scaling
ps$M
```

Compute the median number of recruits
```{r}
## Median number of recruits
prRecruitsQuantileDIB(0.5,ps,mnA=100)
```

Random numbers of recruits are generated from the estimated parameters
```{r}
## Ten random recruit numbers
prRecruitsDIB(10,ps,mnA=100)
```

Check the random numbers of recruits have the required mean
```{r}
## Mean number of recruits
mean(prRecruitsDIB(10000,ps,mnA=100))
```

Simulate the 10000 stochastic age profiles with this distribution of
recruits and check the the observed mean and variance of \(R\) are reproduced
```{r}
## Simulate age profiles and calculate R
N <- matrix(0,10000,ncol(Ms))
for(k in 1:nrow(N))
  N[k,] <- ageStructureS(prRecruitsDIB(ncol(Ms),ps,mnA=100),Msf,ps$M)
R <- N[,3]/rowSums(N[,3:7])
## Estimate mean and variance of R
mean(R,na.rm=TRUE)
var(R,na.rm=TRUE)
```


#### Delta Gamma

The Delta-Gamma model may provide a closer fit to abundance data with
a zero-inflated distribution.

Generate model parameters from the mean and variance of \(R\).  This
computes an estimate of the scaling of natural mortality required to
reproduce the observed \(R\).
```{r}
## Compute model parameters that give mean R = 0.3 and var R = 0.2,
## where R is the proportion of recruits in the population, assuming
## zero recruitment occurs with probability 0.4
ps <- prRecruitParsDG(Msf,mnR=0.3,vrR=0.2,p=0.4)
## Estimated natural mortality scaling
ps$M
```

Compute the median number of recruits
```{r}
## Median number of recruits
prRecruitsQuantileDG(0.5,ps,mnA=100)
```

Random numbers of recruits are generated from the estimated parameters
```{r}
## Ten random recruit numbers
prRecruitsDG(10,ps,mnA=100)
```

Check the random numbers of recruits have the required mean
```{r}
## Mean number of recruits
mean(prRecruitsDG(10000,ps,mnA=100))
```

Simulate the 10000 stochastic age profiles with this distribution of
recruits and check the the observed mean and variance of \(R\) are reproduced
```{r}
## Simulate age profiles and calculate R
N <- matrix(0,10000,ncol(Ms))
for(k in 1:nrow(N))
  N[k,] <- ageStructureS(prRecruitsDG(ncol(Ms),ps,mnA=100),Msf,ps$M)
R <- N[,1]/rowSums(N)
## Estimate mean and variance of R
mean(R,na.rm=TRUE)
var(R,na.rm=TRUE)
```

The non-zero recruits have a scaled Gamma distribution 
```{r}
## Histogram of simulated recruitments
rs <- prRecruitsDG(100000,ps,mnA=100)
hist(rs[rs >0 & rs < 600],seq(0,600,5),freq=FALSE,xlab="Recruits",main="Delta Gamma")
```

But there are many zero recruitment events
```{r}
## Fraction of zero recruitments
mean(rs==0)
```

Repeat for the case where R is the proportion of individuals in age
class 3 as a fraction of individuals of that age or older,
```{r}
## Compute model parameters that give mean R = 0.3 and var R = 0.2,
## where R is the proportion of individual in age class 3 as a
## fraction of individuals that are that age or older, assuming
## recruitment occurs with probability 0.4
ps <- prRecruitParsDG(Msf,mnR=0.3,vrR=0.2,p=0.4,r=3)
## Estimated natural mortality scaling
ps$M
```

Compute the median number of recruits
```{r}
## Median number of recruits
prRecruitsQuantileDG(0.5,ps,mnA=100)
```

Random numbers of recruits are generated from the estimated parameters
```{r}
## Ten random recruit numbers
prRecruitsDG(10,ps,mnA=100)
```

Check the random numbers of recruits have the required mean
```{r}
## Mean number of recruits
mean(prRecruitsDG(10000,ps,mnA=100))
```

Simulate the 10000 stochastic age profiles with this distribution of
recruits and check the the observed mean and variance of \(R\) are reproduced
```{r}
## Simulate age profiles and calculate R
N <- matrix(0,10000,ncol(Ms))
for(k in 1:nrow(N))
  N[k,] <- ageStructureS(prRecruitsDG(ncol(Ms),ps,mnA=100),Msf,ps$M)
R <- N[,3]/rowSums(N[,3:7])
## Estimate mean and variance of R
mean(R,na.rm=TRUE)
var(R,na.rm=TRUE)
```

#### Delta Log Normal

The Delta-Log Normal model may provide a closer fit to abundance data
with a zero-inflated distribution.

Generate model parameters from the mean and variance of \(R\).  This
computes an estimate of the scaling of natural mortality required to
reproduce the observed \(R\).
```{r}
## Compute model parameters that give mean R = 0.3 and var R = 0.2,
## where R is the proportion of recruits in the population, assuming
## zero recruitment events occur with probability 0.4.
ps <- prRecruitParsDLN(Msf,mnR=0.3,vrR=0.1,p=0.4)
## Estimated natural mortality scaling
ps$M
```

Compute the median number of recruits
```{r}
## Median number of recruits
prRecruitsQuantileDLN(0.5,ps,mnA=100)
```

Random numbers of recruits are generated from the estimated parameters
```{r}
## Ten random recruit numbers
prRecruitsDLN(10,ps,mnA=100)
```

Check the random numbers of recruits have the required mean
```{r}
## Mean number of recruits
mean(prRecruitsDLN(10000,ps,mnA=100))
```

Simulate the 10000 stochastic age profiles with this distribution of
recruits and check the the observed mean and variance of \(R\) are reproduced
```{r}
## Simulate age profiles and calculate R
N <- matrix(0,10000,ncol(Ms))
for(k in 1:nrow(N))
  N[k,] <- ageStructureS(prRecruitsDLN(ncol(Ms),ps,mnA=100),Msf,ps$M)
R <- N[,1]/rowSums(N)
## Estimate mean and variance of R
mean(R,na.rm=TRUE)
var(R,na.rm=TRUE)
```

The non-zero recruits have a scaled Log Normal distribution 
```{r}
## Histogram of simulated recruitments
rs <- prRecruitsDLN(100000,ps,mnA=100)
hist(rs[rs >0 & rs < 600],seq(0,600,5),freq=FALSE,xlab="Recruits",main="Delta Log Normal")
```

But there are many zero recruitment events
```{r}
## Fraction of zero recruitments
mean(rs==0)
```

Repeat for the case where R is the proportion of individuals in age
class 3 as a fraction of individuals of that age or older,
```{r}
## Compute model parameters that give mean R = 0.3 and var R = 0.2,
## where R is the proportion of individual in age class 3 as a
## fraction of individuals that are that age or older, assuming
## recruitment occurs with probability 0.4
ps <- prRecruitParsDLN(Msf,mnR=0.3,vrR=0.2,p=0.4,r=3)
## Estimated natural mortality scaling
ps$M
```

Compute the median number of recruits
```{r}
## Median number of recruits
prRecruitsQuantileDLN(0.5,ps,mnA=100)
```

Random numbers of recruits are generated from the estimated parameters
```{r}
## Ten random recruit numbers
prRecruitsDLN(10,ps,mnA=100)
```

Check the random numbers of recruits have the required mean
```{r}
## Mean number of recruits
mean(prRecruitsDLN(10000,ps,mnA=100))
```

Simulate the 10000 stochastic age profiles with this distribution of
recruits and check the the observed mean and variance of \(R\) are reproduced
```{r}
## Simulate age profiles and calculate R
N <- matrix(0,10000,ncol(Ms))
for(k in 1:nrow(N))
  N[k,] <- ageStructureS(prRecruitsDLN(ncol(Ms),ps,mnA=100),Msf,ps$M)
R <- N[,3]/rowSums(N[,3:7])
## Estimate mean and variance of R
mean(R,na.rm=TRUE)
var(R,na.rm=TRUE)
```

