## rescaleProjection

The `rescaleProjection` function rescales an existing projection to
reproduce a prescribed reference abundance or biomass.

Define age classes and within year time steps
```{r}
## Daily time steps and 7 age classes
nsteps <- 365
Ages <- 2:8
Days <- seq(0,1,length=nsteps+1)
h <- 1/nsteps
```

Create matrices of age, length and weight for each time step and age class
```{r}
## Ages
ages <- outer(Days,Ages,FUN="+")
## Age-length and length-weight conversions
ls <- vonBertalanffyAL(ages,t0=0.0667,K=0.5,Linf=500)
ws <- powerLW(ls,9E-10,3.32)
```

Define the normalized intra-annual natural mortality, its integral and the annual scaling
```{r}
## Constant intra-annual natural mortality
ms <- matrix(1,nsteps+1,length(Ages))
ms <- ms/mean(trapz(ms,h))
Ms <- ctrapz(ms,h)
Msf <- final(Ms)
M <- 0.1
```

Create the vector of within year distribution of fishing effort,
assuming fishing occurs on days 80 to 119, and define a length based
selectivity
```{r}
## Normalized within year distribution of fishing effort
fwy <- double(nsteps+1)
fwy[81:220] <- 1
fwy <- fwy/trapz(fwy,h)
## Length based selectivity
ss <- rampOgive(ls,420,30)
```

Define the normalized intra-annual fishing mortality, its integral and
the annual scaling.
```{r}
## Intra-annual fishing mortality - effort by selectivity
fs <- fwy*ss
Fs <- ctrapz(fs,h)
Fsf <- final(Fs)
F <- 0.2
```

Project forward 10 years from a virgin stock assuming constant fishing
mortality, collating annual abundance, biomass and yield.

Create matrices to store annual projections
```{r}
## Ten year projection from virgin stock collating final annual
## abundance, biomass and yield
Years <- 1:10
Nf <- Bf <- Yf <- matrix(NA,length(Years),length(Ages))
```


Compute an equilibrium age structure assuming constant natural mortality
and no fishing, assuming no plus class and 8000 recruits per year.
```{r}
## Deterministic initial age structure assuming no fishing
N0 <- ageStructureD(M*Msf,R=8000)
```

For the first year, project forward from the initial abundance assuming
constant fishing mortality, update the the initial abundance for the
next projection assuming 8000 new recruits, and record the final
abundance, biomass and yield from the projection
```{r}
## Project first year
pr <- project(ws,M*Ms,F*Fs,F*fs,Nref=N0,yield=1)
N0 <- advance(pr$N,R=8000)
Nf[1,] <- final(pr$N)
Bf[1,] <- final(pr$B)
Yf[1,] <- pr$Y
```

As the mortalities are constant from year to year, the projections for
the subsequent years can be computed by rescaling the initial projection
```{r}
## Compute projections for subsequent years by rescaling
for(k in 2:nrow(Nf)) {
  pr <- rescaleProjection(pr,Nref=N0)
  N0 <- advance(pr$N,R=8000)
  Nf[k,] <- final(pr$N)
  Bf[k,] <- final(pr$B)
  Yf[k,] <- pr$Y
}
```

Plot final abundance, biomass and yield for each year by age class
```{r,fig.show="hold"}
## Plot annual abundance, biomass and yield
opar <- par(mfrow=c(2,2),mar=c(5,4,2,2)+0.1)
pal <- hcl(h=seq(15,375,length=8)[1:7],l=65,c=100)
matplot(Years,Nf,xlab="Year",ylab="Abundance",type="l",lty=1,col=pal)
matplot(Years,Bf,xlab="Year",ylab="Biomass",type="l",lty=1,col=pal)
matplot(Years,Yf,xlab="Year",ylab="Yield",type="l",lty=1,col=pal)
par(opar)
```
