## spawningB0D 

The `spawningB0D` function provides a deterministic estimate of the
virgin spawning stock biomass by deterministically computing the
virgin age structure and projecting forward to compute the spawning
biomass.

#### Setup

Define age classes and within year time steps
```{r}
## Daily time steps and 7 age classes
nsteps <- 365
Ages <- 2:8
Days <- seq(0,1,length=nsteps+1)
h <- 1/nsteps
```

Create matrices of age, length and weight for each time step and age class
```{r}
## Ages
ages <- outer(Days,Ages,FUN="+")
## Age-length and length-weight conversions
ls <- vonBertalanffyAL(ages,t0=0.0667,K=0.5,Linf=500)
ws <- powerLW(ls,9E-10,3.32)
```

Define the intra-annual natural mortality, its integral and the annual scaling
```{r}
## Constant intra-annual natural mortality
ms <- matrix(1,nsteps+1,length(Ages))
ms <- ms/mean(trapz(ms,h))
Ms <- ctrapz(ms,h)
Msf <- final(Ms)
M <- 0.128707
```

#### Virgin Spawning Biomass 


Determine the fraction mature at age from length at age
```{r}
## Maturity at age
gs <- rampOgive(ls,410,40)
```

If the spawing period is from day 200 to day 280 (time steps 201 to 281)
```{r}
## Increments in the spawning period
spawn <- 201:281
```
then the deterministic estimate of virgin spawning stock biomass is
```{r}
## Virgin spawning stock abundance
spawningB0D(ws,gs,M*Ms,spawn)
```
