## spawningB0S

The `spawningB0S` function provides a stochastic estimate of the
virgin spawning stock biomass by repeatedly simulating the virgin age
structure and projecting forward to compute the spawning biomass.

#### Setup

Define age classes and within year time steps
```{r}
## Daily time steps and 7 age classes
nsteps <- 365
Ages <- 2:8
Days <- seq(0,1,length=nsteps+1)
h <- 1/nsteps
```

Create matrices of age, length and weight for each time step and age class
```{r}
## Ages
ages <- outer(Days,Ages,FUN="+")
## Age-length and length-weight conversions
ls <- vonBertalanffyAL(ages,t0=0.0667,K=0.5,Linf=500)
ws <- powerLW(ls,9E-10,3.32)
```

Define the intra-annual natural mortality, its integral and the annual scaling
```{r}
## Constant intra-annual natural mortality
ms <- matrix(1,nsteps+1,length(Ages))
ms <- ms/mean(trapz(ms,h))
Ms <- ctrapz(ms,h)
Msf <- final(Ms)
```

#### Random Recruits

Calculate model parameters for the proportional recruitment model
when \(R\) has mean and variance 0.3 and 0.01
```{r}
## Compute model parameters that give mean R = 0.3 and var R = 0.01,
## when R is the proportion of recruits in the population
ps <- prRecruitParsIB(mnR=0.2,vrR=0.01,Msf)
## Estimated natural mortality scaling
ps$M
```

Generate 1000 sets of 10 recruitment events
```{r}
R <- matrix(prRecruitsIB(10000,ps),1000,10)
```


#### Virgin Spawning Biomass 


Determine the fraction mature at age from length at age
```{r}
## Maturity at age
gs <- rampOgive(ls,410,40)
```

If the spawing period is from day 200 to day 280 (time steps 201 to 281)
```{r}
## Increments in the spawning period
spawn <- 201:281
```
then estimates of the median, mean and standard deviation of the
virgin spawning stock biomass are 
```{r}
## Virgin spawning stock abundance
spawningB0S(R,ws,gs,Ms,ps$M,spawn)
```
