## Stock Summary

The `spawningStock` function extracts the spawning stock abundance or
biomass from a projection, while `vulnerableStock` and
`vulnerableStockGYM` extracts abundance or biomass vulnerable to
fishing from a projection.

#### Setup

Define age classes and within year time steps
```{r}
## Daily time steps and 7 age classes
nsteps <- 365
Ages <- 2:8
Days <- seq(0,1,length=nsteps+1)
h <- 1/nsteps
```

Create matrices of age, length and weight for each time step and age class
```{r}
## Ages
ages <- outer(Days,Ages,FUN="+")
## Age-length and length-weight conversions
ls <- vonBertalanffyAL(ages,t0=0.0667,K=0.5,Linf=500)
ws <- powerLW(ls,9E-10,3.32)
```

Define the normalized intra-annual natural mortality, its integral and
the annual scaling 
```{r}
## Constant intra-annual natural mortality
ms <- matrix(1,nsteps+1,length(Ages))
ms <- ms/mean(trapz(ms,h))
Ms <- ctrapz(ms,h)
Msf <- final(Ms)
M <- 0.1
```

Create the vector of within year distribution of fishing effort,
assuming fishing occurs on days 80 to 119, and define a length based
selectivity
```{r}
## Normalized within year distribution of fishing effort
fwy <- double(nsteps+1)
fwy[81:220] <- 1
fwy <- fwy/trapz(fwy,h)
## Length based selectivity
ss <- rampOgive(ls,420,30)
```

Define the normalized intra-annual fishing mortality, its integral and
the annual scaling.
```{r}
## Intra-annual fishing mortality - effort by selectivity
fs <- fwy*ss
Fs <- ctrapz(fs,h)
Fsf <- final(Fs)
F <- 0.2
```

Compute an intial age structure assuming constant mortalities and
assuming no plus class
```{r}
## Deterministic initial age structure
N0 <- ageStructureD(M*Msf,F*Fsf)
N0
```

Project forward for a single year with known mortalities
```{r}
## Annual projection from N0
pr <- project(ws,M*Ms,F*Fs,F*fs,Nref=N0,yield=2)
```

#### Initial and Final

Extract the initial and final abundances in each age class
```{r}
## Initial abundance
initial(pr$N)
## Final abundance
final(pr$N)
```


#### Spawning Stock 


Determine the fraction mature at age from length at age
```{r}
## Maturity at age
gs <- rampOgive(ls,410,40)
```

If the spawning period is from day 200 to day 280 (time steps 201 to 281)
```{r}
## Increments in the spawning period
spawn <- 201:281
```
then the spawning stock abundance and biomass are
```{r}
## Spawning stock abundance
spawningStock(pr$N,gs,spawn)
## Spawning stock biomass
spawningStock(pr$B,gs,spawn)
```

#### Exploitable and Vulnerable Stock

The `exploitableStock` function calculates the mean abundance or
biomass that can be exploited by scaling the abundance or biomass by
selectivity, `vulnerableStock` computes the effort weighted mean
exploitable stock abundance or biomass.

If the exploitable and vulnerable biomass are identical when
fishing effort is constant within the monitoring period
```{r}
## Monitoring period within fishing season
monitor <- 101:151
## Exploitable biomass
exploitableStock(pr$B,ss,monitor)
## Weighted vulnerable biomass
vulnerableStock(pr$B,ss,fwy,monitor)
```
but may differ if the fishing effort varies varies within the
monitoring period
```{r}
## Monitoring period spans fishing season
monitor <- 41:101
## Exploitable biomass
exploitableStock(pr$B,ss,monitor)
## Vulnerable biomass weights by effort
vulnerableStock(pr$B,ss,fwy,monitor)
```

If the monitoring period is outside the fishing season, vulnerable biomasss is zero
```{r}
## No effort in monitoring period
monitor <- 11:31
## Exploitable biomass
exploitableStock(pr$B,ss,monitor)
## Vulnerable biomass weights by effort
vulnerableStock(pr$B,ss,fwy,monitor)
```


