## vonBertalanffyAL

The GYM uses the von Bertalanffy growth curve 
\[
L = L_{\infty} \left ( 1 - e^{-K (A-t_{0})} \right )
\]
to map ages to lengths.

The `vonBertalanffyAL` function implments the von Bertalanffy growth
curve as parameterized in the GYM
```{r}
age <- 2:8

## Convert age to length
len <- vonBertalanffyAL(age,t0=0.0667,K=0.5,Linf=500)
len
```

and `vonBertalanffyLA` is the inverse mapping 
```{r}
## Convert length to age
age <- vonBertalanffyLA(len,t0=0.0667,K=0.5,Linf=500)
age
```


#### Length at age

Define age classes and within year time steps
```{r}
## Daily time steps and 7 age classes
nsteps <- 365
Ages <- 2:8
Days <- seq(0,1,length=nsteps+1)
h <- 1/nsteps
```

Create a matrix of the age at each time step of each age class
```{r}
## Ages
ages <- outer(Days,Ages,FUN="+")
```

Use a von Bertalanffy length at age relationship to create a matrix of
the length at each time step of each age class
```{r}
## Age-length conversion
ls <- vonBertalanffyAL(ages,t0=0.0667,K=0.5,Linf=500)
matplot(Days,ls,type="l",lty=1,xlab="Day",ylab="Length",main="Length at Age")
```

The restriced model assumes that growth is restricted to some fraction
of the year 
```{r}
## Age-length conversion - growth occurs in middle of the year
ls <- vonBertalanffyRAL(ages,t0=0.0667,K=0.5,Linf=500,f0=0.3,f1=0.7)
matplot(Days,ls,type="l",lty=1,xlab="Day",ylab="Length",main="Length at Age")
```
